---
title: "Per Capita and Covid Deaths Explained"
author: "Tom Saunders"
date: "06/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm a bit late to the discussion on Per Capita Graphs and their relation to Covid-19 deaths. Nevertheless, it's been on my mind a while and I wanted to lay out my thoughts on the issue.

## 1. Logarithmic Graphs and Covid

Coivd-19 spreads exponentially, as such it makes sense to chart the graph using logs. Let's take a very simple example, assuming that the **R** of Covid-19 is 2. This means for every 1 person who has the virus they will infect 2 people. If we assume that everyone infects their 2 people in a single say we can represent this matheticaly very easily:
<center>
$N = 2^t$
</center>
Where *N* is the number of people affected and *t* is the number of days since the first infection.

If we model this on a normal graph we get this:
```{r  echo=FALSE}
t = 0:10
n = 2^t
plot(t,n, type="l")

```


Quickly the data becomes impossible to visualise as it increases exponentially. We can manage this with logarithms, this way we can display a wide range of numerical data in a compact way.
<center>
$N = log(2^t)$
</center>

```{r  echo=FALSE}
t = 0:10
logn = t*(log(2))

plot(t,logn, type="l")

```

## 2. How does this relate to Per Capita?

If we were representing this graph as per capita the equation would look like this:
<center>
$N = log($$\frac{2^t}{P}$$)$
</center>
(where P = population)
Using [Logarithmic Identities]() this can be written like this:
<center>
$N = log(2^t) - log(P)$

$N = t*log(2) - log(P)$
</center>

What this means is that adapting for Per Capita in a Logathirithmic graph *only shifts the graph up or down* by a factor of the population but it doesn't change its shape. The most important aspect of the Covid-19 graph is their shape as this can tell you whether a country is peaked, recovering or still in the early stages of the disease. We can visualise this quite easily:



